### Alternate Price Plots | ggplot2 + magrittr

Just some quick experiments with ggplot2 + magrittr to plot prices differently than the traditional ways.  We'll get daily data on the S&P 500 from [FRED](http://research.stlouisfed.org/fred2/) using `getSymbols` and then push it through a `magrittr` pipe to various alternative plots.

A couple notes for those who might be interested in magrittr.  If you want to `->` or `<-` but don't want the pipe fun to end, then you can use `assign` like this.

```{r eval = F}
mydata
  %T>% assign( x="sp_df", value = ., envir = .GlobalEnv ) %>%
```

Also for those who want to use the special `+` inside a pipe or just want your `+` on a different line for tidy code and easy commenting, then you can do like this.

```{r eval =F}
ggplot( ) %>%
  + geom_point()
```

Let me know if I have it all wrong, and now some plots as promised.

```{r message=F, fig.keep='all', fig.width = 8, fig.height = 5 }

require(ggplot2)
require(dplyr)
require(magrittr)
require(quantmod)

getSymbols("SP500", src="FRED", from = "1900-01-01", auto.assign=F) %>%
  na.omit %>%
  data.frame(
    date = index(.)
  ) %T>% assign( x="sp_df", value = ., envir = .GlobalEnv ) %>%
  mutate( year = format(date,"%Y") ) %>%
  ggplot(  aes( x=SP500, group = year ) ) %>%
    + geom_density() %>%
    + facet_wrap(~year,nrow=1) %>% 
    + coord_flip() %>%
    + theme_bw() %>%
    + theme(
        axis.line=element_blank()
        ,axis.text.x=element_blank()
        ,axis.title.x=element_blank()
      ) 

sp_df %>%
  ggplot( aes( x = format(date,"%Y"), y = SP500 ) ) %T>% 
  ( function(x){ print( x + geom_line() ) } ) %T>%
  ( function(x){ print( x + geom_point() ) } ) %T>%
  ( function(x){ print( x + geom_hex( bins = 20 ) ) } ) %>%
  + geom_violin()
                      
```

If you are interested in seeing the source Rmd, then it is [here](http://github.com/timelyportfolio/magrittr_ggplot/).